\documentclass[12pt,courier]{navyletter}

%Sir, thank you very much for the fast reply. I really love what you wrote so far. If you'd like to add more, you could talk about any leadership skills that I portrayed in class. This can then be connected with my leadership billets outside the classroom. Something along the lines of: 
%
%"Andrew showed determination and a deep yearning for pursuing his own projects and ideas. However, his ambitions, as deeply rooted as they were, never came before his humility. He was always keen to advice, humble about his mistakes, and was always ready to adapt and overcome when there were failures in his code or designs. His ability to understand when he was wrong and his enthusiasm to learn from his mistakes not only foreshadows his ability and apt as an engineering student, but also as a leader. Outside the classroom, he has actively participated in leadership billets within his company and throughout the Brigade."  
%
%I think something like this would tie everything together really well, both the academic and military life here at USNA. Also, at the end of the letter, will you be customizing each rec to mention the school's school/major I'm interested in? Thank you again so much. It means the world to be getting this support. 

\usepackage{designature}

\author{Dennis Evangelista}
\title{Letter of recommendation for Andrew Jhu}
\navysubj{Letter of recommendation for MIDN 3/c Andrew Jhu}
%\navyfiling{}
%\navyserial{}
\date{\today}
%\navymarking{}

\begin{document}
\makedateblock{}
\begin{navyletterheader}
\navyfrom{Assistant Professor Dennis Jose Evangelista\newline Department of Weapons \& Systems Engineering}
\navyto{Admissions Board}
\navyskip{}%
\navysubjline%
%\navyskip{}%
%\navyref{refa}{CVN-71 letter Ser 1234, dtd 2 Jan 2016}
%\navyref{refb}{NAVSEA 250-1500-1 Nuclear Welding Manual}
%\navyref{refc}{Bettis letter Ser 5678, dtd 1 Feb 2016}
%\navyencl{encl1}{blah}
\end{navyletterheader}

\section{}
This letter of recommendation is on behalf of MIDN 3/c Andrew Jhu.  Mr.~Jhu was a student in my Introduction to Systems Engineering course, taught to all systems engineering majors. The course focuses on getting students to think like engineers, as well as learn C programming on microcontrollers and Matlab.  Mr.~Jhu is also currently a student in my section for the follow-on class, Principles of Mechatronics.  

\section{} 
Among his highly competitive group of fellow engineering midshipmen, MIDN 3/c Jhu distinguished himself as a team player and creative thinker.  Working on a team, he developed a shoe-shining robot, something that garners high interest here.  Mr. Jhu was the creative force driving his team's video game project, in which players had to stack hamburger ingredients falling from above.  To enable Mr.~Jhu's ideas, I pushed his team to develop fully object-oriented methods for controlling the virtual sandwich ingredients and for interfacing to an external device (a requirement of the project).  Mr.~Jhu was determined to make his ideas work, keen to advice, and ready to adapt and overcome when meeting mistakes or difficulties in his code or his designs.  Every student here at the Academy is required to study some engineering, and the ones like Mr.~Jhu, who do well in their engineering major, are as intense as engineering students at major tech schools.  

\section{}
Over the two terms I have known him, I have been impressed by MIDN 3/c Jhu's creativity and interest in being an engineer.  I am sad to see him leave, as I would have liked to have worked with him on a senior project that would indulge his imaginative mind.  Students here are expected to pursue the highest responsibilities, and Andrew will live up to that in whatever he does.  I believe he would do well as a transfer student in your program, and I am happy to recommend him.  
\\
\noindent\hspace*{4in}\includesignature{}
\signature{D EVANGELISTA}
%\copyto
%File
\end{document}